Unemployment Insurance and Spending

### 2022-02-24 outputs/paper/paper.Rmd
Add files via upload

```{r}
### Loading in cleaned data from R-script in "Scripts" Folder ###

@@

## Tables
```{r spendchangetab, out.extra = '', echo = FALSE}
### Constructing replicated table for Spending Change ###
clean_spendchange |>
  knitr::kable(
    caption = "Spending Change at Unemployment Insurance Exhaustion",
    booktabs = TRUE,
    linesep = "",
  ) |>
  kable_styling(latex_options = "HOLD_position")|>
  column_spec(1:7, color = "black") |>
    row_spec (0, color = "black")
```

```{r spendchangetypetab, out.extra = '', echo = FALSE}
### Constructing spending change table organized by type ###
clean_spendchangtype |>
  knitr::kable(
    caption = "Spending Change at Unemployment Insurance Exhaustion Organized by Spending Type",
    booktabs = TRUE,
    linesep = "",
  ) |>
  kable_styling (latex_options = "HOLD_position") |>
  column_spec (1:7, color = "black") |>
  row_spec (0, color = "black")
```

>>>>

```{r}
### Loading in cleaned data from R-script ###

@@

## Tables
```{r spendchangetab, out.extra = '', echo = FALSE}
### Constructing replicated table for Spending Change ###
clean_spendchange |>
  knitr::kable(
    caption = "Spending Change at Unemployment Insurance Exhaustion",
    booktabs = TRUE,
    linesep = "",
  ) |>
  kable_styling(latex_options = c("HOLD_position", "scale_down"))|>
  column_spec(1:7, color = "black") |>
    row_spec (0, color = "black")
```

```{r spendchangetypetab, out.extra = '', echo = FALSE}
### Constructing spending change table organized by type ###
clean_spendchangtype |>
  knitr::kable(
    caption = "Spending Change at Unemployment Insurance Exhaustion Organized by Spending Type",
    booktabs = TRUE,
    linesep = "",
  ) |>
  kable_styling(latex_options = c("HOLD_position", "scale_down"))|>
  column_spec (1:7, color = "black") |>
  row_spec (0, color = "black")
```
